Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2022-01-05 zhang-cook-laa-langrene-menendez.tex
move paper to the top level directory

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/toy-search}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/toy-interp}

@@

{\centering \includegraphics[width=0.7\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/interrupt}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/polish}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/noisy-better-geo}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/kol-result}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-ferrn/figs/flip-sign}

>>>>

{\centering \includegraphics[width=1\linewidth]{figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{figs/toy-search}

@@

{\centering \includegraphics[width=1\linewidth]{figs/toy-interp}

@@

{\centering \includegraphics[width=0.7\linewidth]{figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{figs/interrupt}

@@

{\centering \includegraphics[width=1\linewidth]{figs/polish}

@@

{\centering \includegraphics[width=1\linewidth]{figs/noisy-better-geo}

@@

{\centering \includegraphics[width=1\linewidth]{figs/kol-result}

@@

{\centering \includegraphics[width=1\linewidth]{figs/flip-sign}
